---
title: "TBonus"
author: "Benjamin Esquinca"
date: "2023-01-24"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

# About the data:

For this analysis I am going to take a database that was given to me, in
which I will explore to determine what this database is, what it talks
about and what I can do with it.

The database is centered on the 2022 date from April 11 to June 14.
Being around 2 months of data.

#### Loading libraries:

```{r}
library('tidyverse') # essential R packages for data science
library('data.table')

library('ggplot2') # visualization
library("ggtext")
library("highcharter")
library('gganimate')

library('dplyr') # data manipulation
library('readr') # input/output
library('skimr') # overview
library('tibble') # data wrangling
library('tidyr') # data wrangling
library('purrr') # data wrangling
library('stringr') # string manipulation
library('forcats') # factor manipulation
library('janitor') # data cleaning
library('scales')
library(DT)
```

#### Load the data: 

```{r}
library(readr)
Assessment_taken_bonuses_export_Sample <- read_csv("Assessment - taken-bonuses-export - Sample.csv")
View(Assessment_taken_bonuses_export_Sample)
```

#### Clean data: 

```{r}
tibble(Assessment_taken_bonuses_export_Sample)

#Let's clean our data first

Assessment_taken_bonuses_export_Sample %>%
  clean_names()


# renaming location to name for mapping
colnames(Assessment_taken_bonuses_export_Sample)[2]<-"name"

Assessment_taken_bonuses_export_Sample$name[Assessment_taken_bonuses_export_Sample$name=="FI"]<- "Finland"
Assessment_taken_bonuses_export_Sample$name[Assessment_taken_bonuses_export_Sample$name=="JP"]<- "Japan"
Assessment_taken_bonuses_export_Sample$name[Assessment_taken_bonuses_export_Sample$name=="NZ"]<- "New Zealand"
Assessment_taken_bonuses_export_Sample$name[Assessment_taken_bonuses_export_Sample$name=="AT"]<- "Austria"
Assessment_taken_bonuses_export_Sample$name[Assessment_taken_bonuses_export_Sample$name=="BE"]<- "Belgium"
Assessment_taken_bonuses_export_Sample$name[Assessment_taken_bonuses_export_Sample$name=="CA"]<- "Canada"
Assessment_taken_bonuses_export_Sample$name[Assessment_taken_bonuses_export_Sample$name=="CH"]<- "Switzerland"
Assessment_taken_bonuses_export_Sample$name[Assessment_taken_bonuses_export_Sample$name=="CK"]<- "Cook Islands"
Assessment_taken_bonuses_export_Sample$name[Assessment_taken_bonuses_export_Sample$name=="CY"]<- "Cyprus"
Assessment_taken_bonuses_export_Sample$name[Assessment_taken_bonuses_export_Sample$name=="CZ"]<- "Czech Republic"
Assessment_taken_bonuses_export_Sample$name[Assessment_taken_bonuses_export_Sample$name=="DE"]<- "Germany"
Assessment_taken_bonuses_export_Sample$name[Assessment_taken_bonuses_export_Sample$name=="IE"]<- "Republic of Ireland"
Assessment_taken_bonuses_export_Sample$name[Assessment_taken_bonuses_export_Sample$name=="LU"]<- "Luxembourg"
Assessment_taken_bonuses_export_Sample$name[Assessment_taken_bonuses_export_Sample$name=="NO"]<- "Norway"
Assessment_taken_bonuses_export_Sample$name[Assessment_taken_bonuses_export_Sample$name=="UA"]<- "Ukraine"


```

With the exploration of data for this analysis, the behavior of the
bonus slots will be determined, by country, provider, and name.

Let's start by exploring the data by country.

# By Country; 

```{r}
#Create the total amount of deposit
Assessment_taken_bonuses_export_Sample$total_deposit <- Assessment_taken_bonuses_export_Sample$number_of_deposits * Assessment_taken_bonuses_export_Sample$deposit_amount


total_cases<-Assessment_taken_bonuses_export_Sample %>%
  select(name, total_deposit) 

total_cases_world <- total_cases %>% 
  group_by(name) %>% 
  summarize(sum_total = sum(total_deposit)) %>% 
  arrange(desc(sum_total)) 
```

Here we can observe the countries that we will be exploring. The first
thing we can see is that Japan is the country with the largest deposit.

```{r}
#Mapping of total deposit

highchart() %>%
  hc_add_series_map(worldgeojson, df = total_cases_world, value = "sum_total", joinBy = "name") %>% 
  hc_legend(enabled = TRUE) %>% 
  hc_add_theme(hc_theme_bloom()) %>% 
  hc_colorAxis(minColor = "lightblue", maxColor="mediumblue") %>% 
  hc_mapNavigation(enabled = TRUE) %>%
  hc_title(text = "World Total Deposit", style = list(fontSize = "25px")) %>%
  hc_subtitle(text="Total Deposit Amount: 27,828", style=list(fontsize = "15px")) %>% 
  hc_add_theme(hc_theme_economist())
```

We have a big difference in the top 3 countries which are: Japan,
Finland and Germany. Taking a considerable advantage against the rest.

```{r}
#Graphic of the cases by country

total_cases_world %>% 
  arrange(desc(sum_total)) %>% 
  slice(1:15)

highchart() %>% 
  hc_chart(type="column", options3d=list(enabled=TRUE, alpha=15, beta=15)) %>% 
  hc_xAxis(categories=total_cases_world $name) %>% 
  hc_add_series(data=total_cases_world$sum_total, name="Country") %>% 
  hc_add_theme(hc_theme_google()) %>% 
  hc_title(text="Total deposit by country") 
```

# Bonus Data;

Here we can see the best bonuses according to your deposited total, the
type of bonus, and the country.

```{r}
#Now let's analyze the bonus data
bonus_data = Assessment_taken_bonuses_export_Sample %>% 
  select(name, bonus_type, bonus_name, provider_name, freespins_campaign_id, slot_name, total_deposit)

by_bonus = bonus_data %>% 
  select(bonus_name, total_deposit,name) %>% 
  group_by(bonus_name)

data = Assessment_taken_bonuses_export_Sample %>% 
  select(name, bonus_type, bonus_name, provider_name, freespins_campaign_id, slot_name, total_deposit)

data %>% 
  select(bonus_name,total_deposit,name,bonus_type) %>% 
  datatable(., options = list(pageLength = 10))

BonusTop20 <- data %>% 
  arrange(desc(total_deposit)) %>% 
  head(n = 20) %>%
  as.data.frame()

BonusTop20 %>% 
  select(bonus_name,total_deposit,name,bonus_type) %>% 
  datatable(., options = list(pageLength = 10))
```

According to the total tables, Japan is the country with the best
bonuses. So their games have better income than any other country.

```{r}
#Let's see the best bonus by deposit
BonusTop20 %>% 
  ggplot(aes(y = bonus_name , x = total_deposit , fill = total_deposit )) +
  geom_bar(stat="identity",position=position_dodge(), alpha = 0.8) + theme_minimal() + 
  scale_fill_gradient(low="#4f908c",high="#6e0ff9") +  theme(legend.position="none")+
  geom_text(aes(label= total_deposit), hjust= -0.2)
```

Now let's take a look at each bonus we had for our top 3 countries:
Japan, Finland and Germany.

```{r}
#Let's take a look to the top 3 country: Japan, Finland and Germany

JapanBonus = subset(by_bonus, name %in% c("Japan"))
FinlandBonus = subset(by_bonus, name %in% c("Finland"))
GermanyBonus = subset(by_bonus, name %in% c("Germany"))
```

#### Japan:

```{r}
JapanBonus %>% 
  ggplot(aes(y = bonus_name , x = total_deposit , fill = total_deposit )) +
  geom_bar(stat="identity",position=position_dodge(), alpha = 0.8) + theme_minimal() + 
  scale_fill_gradient(low="#4f908c",high="#6e0ff9") +  theme(legend.position="none")+
  geom_text(aes(label= total_deposit), hjust= -0.2)
```

#### Finland:

```{r}
FinlandBonus %>% 
  ggplot(aes(y = bonus_name , x = total_deposit , fill = total_deposit )) +
  geom_bar(stat="identity",position=position_dodge(), alpha = 0.8) + theme_minimal() + 
  scale_fill_gradient(low="#4f908c",high="#6e0ff9") +  theme(legend.position="none")+
  geom_text(aes(label= total_deposit), hjust= -0.2)
```

#### Germany:

```{r}
GermanyBonus %>% 
  ggplot(aes(y = bonus_name , x = total_deposit , fill = total_deposit)) +
  geom_bar(stat="identity",position=position_dodge(), alpha = 0.8) + theme_minimal() + 
  scale_fill_gradient(low="#4f908c",high="#6e0ff9") +  theme(legend.position="none")+
  geom_text(aes(label= total_deposit), hjust= -0.2)
```
